Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-10 popl24/ygc.tex
checkpoint

In Figures \ref{fig-ygc-aux} and \ref{fig-ygc-gates} we define a
codebase for Yao's garbled circuits (YGC). This definition follows the
\emph{point-and-permute} method described in \cite{evans2018pragmatic}
and elsewhere, to which the reader is referred for more in-depth discussion.
In this implementation client 2 is the \emph{garbler} and
client 1 is the \emph{evaluator}. The garbler builds the garbled
tables and shares them with the evaluator, who then evaluates
the gate in an oblivious fashion until the final public output is
generated through decryption. This definition is well-typed,
with input type annotations for top-level functions listed in
Figure \ref{fig-ygc-types}.

>>>>

In Figures \ref{fig-ygc-aux} and \ref{fig-ygc-gates} we define a
codebase for Yao's garbled circuits (YGC). This definition follows the
\emph{point-and-permute} method described in \cite{evans2018pragmatic}
and elsewhere, to which the reader is referred for more in-depth
discussion.  In this implementation client 2 is the \emph{garbler} and
client 1 is the \emph{evaluator}. The garbler builds the garbled
tables and shares them with the evaluator, who then evaluates the gate
in an oblivious fashion until the final public output is generated
through decryption. Our certification method leverages this definition
of compositional units comprising complete related subprotocols--
i.e., both the garbler's construction of the gates and the evaluator's
evaluation of them. However, we note that our formal results are applicable
to the YGC style where the garbler shares the entire circuit prior to
evaluation. Our implementation is well-typed, with input type annotations
for top-level functions listed in Figure \ref{fig-ygc-types}.
